\bf Landslide: Systematic Testing in 15-410 \\ User Guide

### 2016-04-14 irb/infosheet.tex
Update infosheet and survey for landslide study
Add another fall 2014 note - commented out - in irb info sheet
update irb forms slightly
update irb stuff, stale changes lying around in my git diff

{\bf Risks.}
We expect the risks and discomfort associated with participation in this study to be no greater than those ordinarily encountered while working on 15-410 class projects.
As always with concurrent programming, it is possible to spend a lot of time looking for a bug with no meaningful result, while that time could otherwise have been spent on project implementation.
However, as Landslide is a research tool still under development, it is also possible that a bug in Landslide itself may produce a misleading error report. We expect you to protect yourself by responsibly allocating time between using Landslide and working on P2 normally.
\\

\noindent {\bf Benefits.}
Because we are providing you with a more powerful testing tool during P2 than you would normally have access to, we hope you will be able to find and fix bugs faster, resulting in a higher grade.

@@

During this study we will collect personally identifiable information from you as follows. While you use Landslide, it will automatically record your activity in terms of commands issued, time spent running tests, bug reports, and snapshots of your code. We will also collect paper surveys which you will fill out while using Landslide.
Carnegie Mellon may be required to disclose personally identifiable information as required by law, regulation, subpoena or court order.
Otherwise, we will protect your confidentiality as follows:

\begin{itemize}
	\item Data collected by Landslide will be stored in AFS accessible only to Ben Blum and Garth Gibson.
	\item Paper surveys will be stored in a locked filing cabinet accessible only to Ben Blum and Garth Gibson.
	\item Within one semester after the study, we will destroy all personally identifying information, keeping only anonymized and aggregate results.
	\item Professor Eckhardt will have access to study data only after final semester grades are submitted. Other members of course staff will never have access to study data. Course staff may, however, use Landslide on your final submitted code on their own.
\end{itemize}

\section{Your Rights}
There is no coercion or deception associated with this study.
Your participation is voluntary.
You are free to stop your participation at any point; likewise, the Principal Investigator may at his discretion remove you from the study.
Refusal to participate or discontinued participation in the study will not result in any penalty or loss of benefits or rights to which you might otherwise be entitled.
Your participation or lack thereof will have no impact in your 15-410 class grade, except as it might (hopefully) help you write better code.
\\

>>>>

{\bf Risks.}
We expect the risks and discomfort associated with participation in this study to be no greater than those ordinarily encountered while working on 15-410 class projects.
As always with concurrent programming, it is possible to spend a lot of time looking for a bug with no meaningful result, while that time could otherwise have been spent on project implementation.
However, as Landslide is a research tool still under development, it is also possible that a bug in Landslide itself may produce a misleading error report. We expect you to protect yourself by responsibly allocating time between using Landslide and working on P2 normally. It is expected that participation in this study will require from 2 to 8 hours of active work, depending on bug-finding results.
\\

\noindent {\bf Benefits.}
Because we are providing you with a more powerful testing tool during P2 than you would normally have access to, we hope you will be able to find and fix bugs faster, resulting in a higher grade.
%\\
%
%\noindent {\bf FALL 2014 NOTE}: As this semester we are conducting a preliminary study on a ``for fun'' basis, at the end of the semester rather than during P2, there will be no impact on your grade. 15-410 staff will not accept patches based on your findings with Landslide.

@@

During this study we will collect personally identifiable information from you as follows. While you use Landslide, it will automatically record your activity in terms of commands issued, time spent running tests, bug reports, and snapshots of your code.
%We will also collect paper surveys which you will fill out while using Landslide.
Carnegie Mellon may be required to disclose personally identifiable information as required by law, regulation, subpoena or court order.
Otherwise, we will protect your confidentiality as follows:

\begin{itemize}
	\item Data collected by Landslide will be stored in AFS accessible only to Ben Blum and Garth Gibson.
	%\item Paper surveys will be stored in a locked filing cabinet accessible only to Ben Blum and Garth Gibson.
	\item Within one semester after the study, we will destroy all personally identifying information, keeping only anonymized and aggregate results.
	\item Professor Eckhardt will have access to study data only after final semester grades are submitted. Other members of course staff will never have access to study data. Course staff may, however, use Landslide on your final submitted code on their own.
\end{itemize}
%
%\noindent {\bf FALL 2014 NOTE}: This semester, Landslide's automatic data collection is not implemented. We will rely on you to supply commands issued and time spent in the survey section, and to submit Landslide's bug reports and snapshots of your code in a tarball of your workspace.

\section{Your Rights}
There is no coercion or deception associated with this study.
Your participation is voluntary.
You must be 18 years of age or older to participate.
You are free to stop your participation at any point; likewise, the Principal Investigator may at his discretion remove you from the study.
Refusal to participate or discontinued participation in the study will not result in any penalty or loss of benefits or rights to which you might otherwise be entitled.
Your participation or lack thereof will have no impact in your 15-410 class grade, except as it might (hopefully) help you write better code.
\\

### 2016-04-14 irb/survey.tex
update irb stuff, stale changes lying around in my git diff

\title{\bf Landslide: Systematic Testing in 15-410 \\ User Guide and Survey}
\author{Ben Blum}
\date{}
\maketitle

@@

The very first thing you should do is {\bf READ THIS DOCUMENT ENTIRELY FIRST!} We need you to print out several survey sheets before you dive in.
\\

@@

\begin{enumerate}
	\item Clone the repository -- {\tt git clone https://github.com/bblum/landslide.git} -- this will be your workspace.
	\item Run {\tt ./p2-setup.sh PATH}, where {\tt PATH} is the absolute path to your p2 implementation.
		\begin{itemize}
			\item This command will import your p2 into {\tt ./pebsim/p2-basecode/} and then attempt to build it.
			\item {\tt PATH} should be the path with {\tt 410kern}, {\tt 410user}, {\tt user/libthread}, etc as subdirectories, not the {\tt user/libthread} directory itself.
		\end{itemize}
	\item Next, make sure you have read this document entirely. At this point you should have several survey sheets printed out, ready to write on -- see the Survey section below. You should also have some means of timing yourself.
	\item Run {\tt ./landslide OPTIONS} to run tests with Landslide. {\bf Fill out a fresh survey sheet each time you do this.} Repeat until satisfied.
		\begin{itemize}
			\item Use {\tt ./landslide -h} to view command line options. The most important ones are {\tt -t}, max testing time, and {\tt -p}, which test program to run.
				% TODO: Remove this TODO when you have implemented glue to move the html files to the toplevel directory.
			\item Landslide's bug reports will show up as HTML files. If you are using a cluster machine in person, you can view them by pointing a browser to {\tt file:///PATH/TO/landslide/FILENAME.html}.
				\footnote{Another option: move it to {\tt \textasciitilde/www} in your AFS, and view it at {\tt http://www.contrib.andrew.cmu.edu/\textasciitilde{}YOUR\_ANDREWID/FILENAME.html}. Note the {\tt www} in the URL is mandatory; note also that this will allow the world to see it, so be careful!}
				\footnote{If you have your own custom test case, you can put it in {\tt pebsim/p2-basecode/user/progs} and edit \\ {\tt pebsim/p2-basecode/config.mk} to build it, then run {\tt ./p2-setup.sh} again.}
			\item The available test programs are {\tt thr\_exit\_join} (the default), {\tt broadcast\_test}, {\tt paraguay}, and {\tt rwlock\_downgrade\_read\_test}.
			\item The suggested sequence of test configurations to run is as follows. You can, of course, change the time limits or test programs as you see fit. For the longer-running configurations, it's recommended to run them inside of a {\tt screen} session.
			\begin{itemize}
				\item {\tt ./landslide -p thr\_exit\_join -t 30m}
				\item {\tt ./landslide -p broadcast\_test -t 30m}
				\item {\tt ./landslide -p paraguay -t 30m}
				\item {\tt ./landslide -p rwlock\_downgrade\_read\_test -t 30m}
				\item {\tt ./landslide -p thr\_exit\_join -t 3h}
				\item {\tt ./landslide -p broadcast\_test -t 3h}
				\item {\tt ./landslide -p paraguay -t 3h}
				\item {\tt ./landslide -p rwlock\_downgrade\_read\_test -t 3h}
				\item {\tt ./landslide -p thr\_exit\_join -t 12h}
				\item {\tt ./landslide -p broadcast\_test -t 12h}
				\item {\tt ./landslide -p paraguay -t 12h}
				\item {\tt ./landslide -p rwlock\_downgrade\_read\_test -t 12h}
			\end{itemize}
		\end{itemize}
\end{enumerate}

@@

\newpage

\section{Survey}
\subsection{Overall Survey Questions}

\begin{center}
{\bf Print this page out once.}
\end{center}

\begin{enumerate}
	\item How much time did you spend directly using Landslide? This includes configuring test parameters and interpreting debug output. It does not include time spent running Landslide in the background, e.g. overnight.
		\vspace{0.5in}

	\item What test configurations did you use that DIDN'T find bugs? For example, {\tt ./landslide -t 15m -p thr\_exit\_join}
\end{enumerate}

\newpage
\subsection{Per-Bug Survey Questions}
\begin{center}
{\bf \large PRINT OUT THIS PAGE MULTIPLE TIMES.
\\

Each time you find a new bug with Landslide, fill this out again.}
\end{center}

\begin{enumerate}
		% TODO: find a way to allow ze studence to condense non-bug-finding runs onto 1 page.
	\item What test configuration did you use? For example, {\tt ./landslide -t 15m -p thr\_exit\_join}
		\vspace{0.5in}
	\item Summarize the bug.
		\vspace{2in}
	\item How IMPORTANT was this bug? Rate on a scale from 1 to 10, where:
		\begin{itemize}
			\item 1 = Trivial; an obvious ``oops'' that does not reflect any key lessons learned during the project. I would expect to not lose any points for this bug.
			\item 4 = Minor; a logic problem not related to threads/synchronization. I would expect to lose 1 or 2 points at most for this bug.
			\item 7 = Major; a concurrency-related bug related to subject matter discussed in lecture.
			\item 10 = Severe; this bug reflects a fundamental lesson about concurrency that we learned during the project. I would expect to receive ``see course staff'' in my ink if I turned in code with this bug!
		\end{itemize}
		\vspace{0.2in}
	\item How much EFFORT/TIME did this bug require to diagnose and fix? Rate on a scale from 1 to 10, where:
		\begin{itemize}
			\item 1 = Very little; we knew immediately what was wrong and needed to change only 1 or 2 lines of code.
			\item 5 = Some; the bug took considerable thought to fix, and required nontrivial code changes.
			\item 10 = Lots; we worked for several hours to fix the bug and/or required a major refactoring of our code.
		\end{itemize}
		\vspace{0.2in}
	\item How likely would a CONVENTIONAL STRESS TEST be able to find the bug (i.e., running the program repeatedly, not using Landslide)? Rate on a scale from 1 to 10, where:
		\begin{itemize}
			\item 1 = No hope. The window for a random timer interrupt to expose the bug is so small that a conventional stress test could easily run continuously overnight without encountering it.
			\item 5 = Moderate chance. Most random timer interrupts would not expose the bug, but the window is more than just a few instructions.
			\item 10 = Very likely. A random timer interrupt during the test would expose the bug more often than not.
		\end{itemize}
\end{enumerate}

>>>>

\title{\bf Landslide: Systematic Testing in 15-410 \\ User Guide
%and Survey
}
\author{Ben Blum}
\date{}
\maketitle

@@

%The very first thing you should do is {\bf READ THIS DOCUMENT ENTIRELY FIRST!} We need you to print out several survey sheets before you dive in.
%\\

@@

\begin{enumerate}
	\item Clone the repository -- {\tt git clone https://github.com/bblum/landslide.git} -- this will be your workspace.
	\item Run {\tt ./p2-setup.sh PATH}, where {\tt PATH} is the absolute path to your p2 implementation.
		\begin{itemize}
			\item This command will import your p2 into {\tt ./pebsim/p2-basecode/} and then attempt to build it.
			\item {\tt PATH} should be the path with {\tt 410kern}, {\tt 410user}, {\tt user/libthread}, etc as subdirectories, not the {\tt user/libthread} directory itself.
		\end{itemize}
	%\item Next, make sure you have read this document entirely. At this point you should have several survey sheets printed out, ready to write on -- see the Survey section below. You should also have some means of timing yourself.
	\item Run {\tt ./landslide OPTIONS} to run tests with Landslide, for various values of {\tt OPTIONS}:
		%{\bf Fill out a fresh survey sheet each time you do this.} Repeat until satisfied.
		\begin{itemize}
			\item Use {\tt ./landslide -h} to view command line options. The most important ones are {\tt -t}, max testing time, and {\tt -p}, which test program to run.
				% TODO: Remove this TODO when you have implemented glue to move the html files to the toplevel directory.
			\item Landslide's bug reports will show up as HTML files. If you are using a cluster machine in person, you can view them by pointing a browser to {\tt file:///PATH/TO/landslide/FILENAME.html}.
				\footnote{For remote usage: move it to {\tt \textasciitilde/www} in your AFS, and view it at {\tt http://www.contrib.andrew.cmu.edu/\textasciitilde{}YOUR\_ANDREWID/FILENAME.html}. Note the {\tt www} in the URL is mandatory; note also that this will allow the world to see it, so be careful!}
			\item The available test programs are {\tt thr\_exit\_join} (the default), {\tt mutex\_test}, {\tt paradise\_lost}, \\ {\tt broadcast\_test}, {\tt paraguay}, and {\tt rwlock\_downgrade\_read\_test}.
				\footnote{If you have your own custom test case, you can put it in {\tt pebsim/p2-basecode/user/progs} and edit \\ {\tt pebsim/p2-basecode/config.mk} to build it, then run {\tt ./p2-setup.sh} again.}
			\item The suggested sequence of test configurations to run is as follows. You can, of course, change the time limits or test programs as you see fit. For the longer-running configurations, it's recommended to run them inside of a {\tt screen} session.
			\begin{itemize}
				\item {\tt ./landslide -p thr\_exit\_join -t 30m}
				\item {\tt ./landslide -p mutex\_test -t 30m}
				\item {\tt ./landslide -p paradise\_lost -t 30m}
				\item {\tt ./landslide -p broadcast\_test -t 30m}
				\item {\tt ./landslide -p paraguay -t 30m}
				\item {\tt ./landslide -p rwlock\_downgrade\_read\_test -t 30m} \\
				\item {\tt ./landslide -p thr\_exit\_join -t 3h}
				\item {\tt ./landslide -p mutex\_test -t 3h}
				\item {\tt ./landslide -p paradise\_lost -t 3h}
				\item {\tt ./landslide -p broadcast\_test -t 3h}
				\item {\tt ./landslide -p paraguay -t 3h}
				\item {\tt ./landslide -p rwlock\_downgrade\_read\_test -t 3h} \\
				\item {\tt ./landslide -p thr\_exit\_join -t 12h}
				\item {\tt ./landslide -p mutex\_test -t 12h}
				\item {\tt ./landslide -p paradise\_lost -t 12h}
				\item {\tt ./landslide -p broadcast\_test -t 12h}
				\item {\tt ./landslide -p paraguay -t 12h}
				\item {\tt ./landslide -p rwlock\_downgrade\_read\_test -t 12h}
			\end{itemize}
		\end{itemize}
\end{enumerate}

@@

%\newpage
%
%\section{Survey}
%\subsection{Overall Survey Questions}
%
%\begin{center}
%{\bf Print this page out once.}
%\end{center}
%
%\begin{enumerate}
%	\item How much time did you spend directly using Landslide? This includes configuring test parameters and interpreting debug output. It does not include time spent running Landslide in the background, e.g. overnight.
%		\vspace{0.5in}
%
%	\item What test configurations did you use that DIDN'T find bugs? For example, {\tt ./landslide -t 15m -p thr\_exit\_join}
%\end{enumerate}
%
%\newpage
%\subsection{Per-Bug Survey Questions}
%\begin{center}
%{\bf \large PRINT OUT THIS PAGE MULTIPLE TIMES.
%\\
%
%Each time you find a new bug with Landslide, fill this out again.}
%\end{center}
%
%\begin{enumerate}
%		% TODO: find a way to allow ze studence to condense non-bug-finding runs onto 1 page.
%	\item What test configuration did you use? For example, {\tt ./landslide -t 15m -p thr\_exit\_join}
%		\vspace{0.5in}
%	\item Summarize the bug.
%		\vspace{2in}
%	\item How IMPORTANT was this bug? Rate on a scale from 1 to 10, where:
%		\begin{itemize}
%			\item 1 = Trivial; an obvious ``oops'' that does not reflect any key lessons learned during the project. I would expect to not lose any points for this bug.
%			\item 4 = Minor; a logic problem not related to threads/synchronization. I would expect to lose 1 or 2 points at most for this bug.
%			\item 7 = Major; a concurrency-related bug related to subject matter discussed in lecture.
%			\item 10 = Severe; this bug reflects a fundamental lesson about concurrency that we learned during the project. I would expect to receive ``see course staff'' in my ink if I turned in code with this bug!
%		\end{itemize}
%		\vspace{0.2in}
%	\item How much EFFORT/TIME did this bug require to diagnose and fix? Rate on a scale from 1 to 10, where:
%		\begin{itemize}
%			\item 1 = Very little; we knew immediately what was wrong and needed to change only 1 or 2 lines of code.
%			\item 5 = Some; the bug took considerable thought to fix, and required nontrivial code changes.
%			\item 10 = Lots; we worked for several hours to fix the bug and/or required a major refactoring of our code.
%		\end{itemize}
%		\vspace{0.2in}
%	\item How likely would a CONVENTIONAL STRESS TEST be able to find the bug (i.e., running the program repeatedly, not using Landslide)? Rate on a scale from 1 to 10, where:
%		\begin{itemize}
%			\item 1 = No hope. The window for a random timer interrupt to expose the bug is so small that a conventional stress test could easily run continuously overnight without encountering it.
%			\item 5 = Moderate chance. Most random timer interrupts would not expose the bug, but the window is more than just a few instructions.
%			\item 10 = Very likely. A random timer interrupt during the test would expose the bug more often than not.
%		\end{itemize}
%\end{enumerate}
